%-------------------------
% Resume in LaTeX
% Author : Geeth Tunuguntla
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/geeth-tunuguntla/}{\Large Geeth Tunuguntla}{ | Computer Engineering Student}} & Email : \href{mailto:gtunux@gmail.com}{gtunux@gmail.com}\\
     & Mobile : +1-630-923-1733 \\

\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Texas A\&M University}{College Station, TX}
      {Bachelor of Engineering in Computer Science}{Aug. 2018 -- May. 2022}
      % ;  GPA: 4.00 next to major description
        \resumeItemListStart
   \resumeItem{PBE}{Involved in Professional Brotherhood of Engineering}
   \resumeItem{Texas Aggie Game Development}{Create games using Cryengine \& Unity coupled with Adobe Maya Graphic design}
   \resumeItem{ResLife}{Programming chair for Appelt Hall}
   \resumeItemListEnd
   \resumeSubheading
      {Hinsdale Central High School}{Hinsdale, IL}
      {High School Diploma}{August 2014 -- May 2018}
    \resumeSubHeadingListEnd

 


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Texas A\&M University: Dr.Atlas Wang}{College Station, TX}
      {Undergraduate Research}{April 2019 - Present}
      \resumeItemListStart
        \resumeItem{PyTorch}
          {PyTorch is an open source machine learning library. Our team used it to research image 		processing working with MoodMe to break down pixels in an image to recognize key facial 		features and determine emotion.}
      \resumeItemListEnd

    \resumeSubheading
      {Texas A\&M Engineering Dept.}{College Station, TX}
      {Teaching and Lab Assistant}{Aug 2019 - Dec 2019}
      \resumeItemListStart
        \resumeItem{Teaching Assistant - ENGR 102 - Python Course }
          {Proctored exams and weekly quizzes in class of 104 students. Graded exams, quizzes, and 		homework using debug algorithm made in python 3.7. Held office hours every week for open		student Q\&A sessions, coupled with exam prep sessions.}
       \resumeItemListEnd

    \resumeSubheading
      {Acquainted(ACQ) }{West Lafayette, IN}
      {Project Lead}{September 2018 - Present}
      \resumeItemListStart
        \resumeItem{Project Managment}
          {Created models for price \& sponsorship forecasting, manage IT teams.}
        \resumeItem{Django }
          {Utilized python backend for a web application used for dynamic web apps such as ACQ.}
        \resumeItem{Adobe PhoneGap}
          {Imported project HTML CSS, and JavaScript to be transcribed into swift for iOS app store 		publication.}
      \resumeItemListEnd

    \resumeSubheading
      {Brighton Collectibles}{Oakbrook, IL}
      {Part-time Sales Associate}{Dec 2018 - Jan 2019; Dec 2019 - Jan 2020}
      \resumeItemListStart
          \resumeItem{Data Management}
          {Monitored and maintained cloud based KWI system. Handled finances, and record keeping}
       	 \resumeItem{Sales Associate}
          {Interacted with customers on the floor to sell luxury accessories}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{ACQ; Current}
      {Swift based application to optimize job searching time}
    \resumeSubItem{Facial Analysis Research; Current}
      {Machine Learning research using PyTorch library with Dr.Atlas Wang}
    \resumeSubItem{Marauders App; Past}
      {Developed a web-based app for my soccer team, Marauder FC, app was used for live field updates 	and scheduling }
  \resumeSubHeadingListEnd
  
  %-----------Certifications-----------------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubItem{NVIDEA Deep Learning For Computer Vision}
      {Feb 2019}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
 \resumeSubItem{Languages}
 {Python, Javascript, C++, Java, HTML \& CSS, Swift, SQL(Learning)}
 \resumeSubItem{Technologies}
 {Adobe PhoneGap, Cryengine, Unity, Autodesk inventor \& Maya, Excel}
 \resumeSubHeadingListEnd
 
 %--------Awards----------
\section{Awards}
 \resumeSubHeadingListStart
 \resumeSubItem{Eagle Scout}
 {Aug 2017 | Boy Scouts Troop 10 }
 \resumeSubItem{Illinois State Scholar's Award}
 {Dec 2017}
 \resumeSubItem{Maroon Scholarship Award}
 {Feb 2018}
  \resumeSubItem{AP Scholar}
 {May 2018}
 \resumeSubHeadingListEnd
 
  %--------Additional Information----------
\section{Additional Information}
 \resumeSubHeadingListStart
 \resumeSubItem{\href{https://github.com/GTunuFu}{GitHub}}
 {https://github.com/GTunuFu}
 \resumeSubItem{Date of Birth}
 {2000-09-11}
  \resumeSubItem{Citizenship Status}
 {US Citizen}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
